Price of Anarchy for Mean Field Games

### 2018-07-31 PoA_response_to_referee.tex

\begin{document}

\maketitle

We would like to thank the reviewer for their remarks. We have addressed each of their points as follows:\\

\hspace{-7mm} \textbf{Main Points:}
\begin{enumerate}
	\item This was a good suggestion. We have added equations (3)-(7) on page 7, and equations (9)-(13) on page 8, and we refer to these equations often. In the same vein we have added equations (26)-(29) on pages 13-14, which are used frequently in Propositions 3-7.
	\item Since the Hamiltonian depends on the scalars $\bar{\mu}$ and $\bar{\nu}$, instead of the full measures, the derivative in the measure argument greatly simplifies. On page 8 line 6, we refer to section 4 in [5], where they write what this condition should be in the linear quadratic case. On page 8 lines 7 and 8, the derivative is a standard derivative and does not need explaining further. There was a typo in the previous version that may have caused confusion, where we mistakenly wrote $\partial_{\mu}$ instead of $\partial_{\bar{\mu}}$.
	\item 
	\item Yes, it is correct that there is a square in the definitions of $C^w$ and $D^w$ that doesn't appear in the definitions of $C^u$ and $C^w$. This was overlooked by the authors. If we were to rewrite Corollary 3 with the correct condition to have $(A^u,B^u,C^u,D^u)=(A^w,B^w,C^w,D^w)$, it would not be substantially different from Corollary 1 and thus, we dropped Corollary 3.
	\item
	\item
	\item We added a sentence at the beginning of section 2.4 on page 27 stating that we use a simple rectangular integration rule to numerically compute integrals.
\end{enumerate}

### 2018-07-31 PoA.tex
response to referee: some of the major points

\subsection{\textbf{Numerical Results}}
The solutions to the problems we have considered are given by the formulas derived in Appendix \ref{appendix_solving_fbsdes}, which are explicit up to evaluating integrals. Using the simple rectangle rule to evaluate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, non-negative, and satisfy assumption \ref{assumption}. In particular, when we allow for full interaction (i.e. through the states and the controls), we choose the following default values:

>>>>

\subsection{\textbf{Numerical Results}}
The solutions to the problems we have considered are given by the formulas derived in Appendix \ref{appendix_solving_fbsdes}, which are explicit up to evaluating integrals. Using the simple rectangle rule to estimate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, non-negative, and satisfy assumption \ref{assumption}. In particular, when we allow for full interaction (i.e. through the states and the controls), we choose the following default values:
